### 2018-09-14 99_Anexos/MilStd105E.Rmd
Completed "IntroduccionAR". Started "IntroCalidad" and "Anexos". Imporoved README.md. Created compilation script

---
output:
  revealjs::revealjs_presentation:
    theme: simple
    slide_level: 2
    highlight: pygments
    center: false
    self_contained: true
    css: "../css/styles.css"
    reveal_options:
      slideNumber: true
      previewLinks: false
      transition: 0
      background_transition: 0
---

>>>>

---
output:
  revealjs::revealjs_presentation:
    theme: simple
    slide_level: 2
    highlight: pygments
    center: false
    self_contained: true
    css: "../css/styles.css"
    reveal_options:
      slideNumber: true
      previewLinks: false
      transition: 0
      background_transition: 0
editor_options: 
  chunk_output_type: console
---
